### 2018-04-18 paper.Rmd
exclude german child

Our `transcript_by_speaker` table contains multiple derived measures of lexical diversity -- here we used MTLD [@mccarthy2005assessment].
MTLD is derived from the average length of continuous text units above a certain type-token ratio, making it relatively robust to transcript length.
We start by filtering those children for which a sex was defined, who speak a language in our subset, and are in the appropriate age range.
We then average their MTLD score across transcripts after having grouped the data by child, age, sex, and language.

```{r echo=TRUE}
data <- stats %>%
  filter(!is.na(target_child_sex),
         language %in% included_languages) %>%
  group_by(target_child_id, target_child_age, target_child_sex, language) %>%
  summarise(measure = mean(mtld)) %>%
  ungroup() %>%
  mutate(age_years = target_child_age / 365,
         target_child_sex = factor(target_child_sex, levels = c("male","female"))) %>%
  filter(age_years < max_age)
```

>>>>

Our `transcript_by_speaker` table contains multiple derived measures of lexical diversity -- here we used MTLD [@mccarthy2005assessment].
MTLD is derived from the average length of continuous text units above a certain type-token ratio, making it relatively robust to transcript length.
We start by filtering those children for which a sex was defined, who speak a language in our subset, and are in the appropriate age range.
We then average their MTLD score across transcripts after having grouped the data by child, age, sex, and language.
One child in particular contained transcripts that were a collection of his most complex utterances (recorded by the parents); this child was excluded from the analysis.

```{r echo=TRUE}
data <- stats %>%
  filter(!is.na(target_child_sex),
         language %in% included_languages) %>%
  group_by(target_child_id, target_child_age, target_child_sex, language) %>%
  summarise(measure = mean(mtld)) %>%
  ungroup() %>%
  mutate(age_years = target_child_age / 365,
         target_child_sex = factor(target_child_sex, levels = c("male","female"))) %>%
  filter(age_years < max_age, target_child_name != 9387)
```
